---
title: "Coghill Research - Disk quota exceeded"
subtitle: "Directory Size analysis"
author: "Nathan W. Van Bibber"
date: "`r format(Sys.Date(), format = '%m-%d-%Y')`"
params:
  show_code: false
  run_counts: false
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    df_print: paged
    code_folding: hide
    theme: flatly
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = params$show_code,
                      message = FALSE,
                      # results = "hide",
                      warning = FALSE,
                      comment = "",
                      fig.align='center'
                      )
```


```{r}
library(fs)
library(here)
library(tidyverse)
library(reactable)
```

```{r eval=params$run_counts}
if (params$run_counts) {
  coghill_research <- 
    fs::dir_info("//hlm/data/project/Coghill_Research", recurse = F)
}
```


```{r eval=FALSE}
if (FALSE) {
  path_prostate <- 
    coghill_research %>% 
    filter(str_detect(path, "prostate")) %>% 
    pull(path)
  
  prostate_cancer_proj <- 
    dir_info(path = path_prostate, recurse = T)
  
  prostate_cancer_proj %>% 
    summarise(
      total_size = sum(size, na.rm = T)
    )
}
```


```{r}
if (params$run_counts) {
  
  coghill_research_recurse <- 
    coghill_research %>% 
    filter(type == "directory") %>% 
    mutate(
      directory = str_remove(path, "//hlm/data/project/Coghill_Research/"), 
      path_0 = path,
      .before = 0L
    ) %>% 
    ## test with only a few directories
    # filter(str_detect(directory, "prostate")|str_detect(directory, "Grace")) %>%
    # group_by(directory) %>% 
    nest(
      .by = c(directory, path_0),
      .key = "dir_info_0"
    ) %>% 
    mutate(
      dir_info = map(path_0, ~ dir_info(.x, recurse = TRUE))
    )
  
  file_name <- paste0(Sys.Date(), "_coghill_research_recurse", ".rds")

  write_rds(coghill_research_recurse, here("data/tidy_data", file_name))
  
} else {
  coghill_research_recurse <- 
    read_rds(here("data/tidy_data", "2024-08-07_coghill_research_recurse.rds"))
}
```

<br>

# Top-level directory size

Currently, there are `r nrow(coghill_research_recurse)` top-level directories in 
*Coghill_Research*. Here are the largest files using more than 1GB of storage space.

```{r}
coghill_research_recurse %>% 
  unnest(dir_info) %>% 
  summarise(
    n_files = n(),
    total_size = sum(size, na.rm = T),
    .by = directory
  ) %>% 
  arrange(desc(total_size)) %>%
  filter(total_size > fs_bytes("1G")) %>% 
  gt::gt() %>% 
  # gt::cols_width(
  #   n_files ~ px(120),
  #   total_size ~ px(120)
  # ) %>% 
  gt::cols_align(align = "right", columns = total_size) 
```

<br>

It looks like *ORIEN_HIV (MCC 21527)* is the culprit!

<br>

## ORIEN sub-sirectories

```{r}
coghill_research_recurse_subdir <- 
  coghill_research_recurse %>% 
  unnest(dir_info) %>% 
  filter(str_detect(directory, "ORIEN")) %>%
  # filter(type == "directory") %>% 
  # count(path) %>% count(n)
  mutate(
    sub_directory = str_remove(path, "//hlm/data/project/Coghill_Research/ORIEN_HIV \\(MCC 21527\\)/"),
    # path = str_remove(path, "//hlm/data/project/Coghill_Research/ORIEN_HIV (MCC 21527)/")
    .before = 0L
  ) %>% 
  separate_wider_delim(sub_directory, delim = "/", names_sep = "", too_few = "align_start")

```


WES and RNAseq data in *Orien_21PRJ081MCC* and *21PRJ108MCC_Coghill* use up almost 
all of the available disk space.

<br>

```{r eval=FALSE}
coghill_research_recurse_subdir %>% 
  summarise(
    n_files = n(),
    total_size = sum(size, na.rm = T),
    .by = sub_directory1
  ) %>% 
  arrange(desc(total_size)) %>% 
  filter(n_files > 1)
```

```{r}
coghill_research_recurse_subdir %>% 
  summarise(
    n_files = n(),
    total_size = sum(size, na.rm = T),
    .by = c(sub_directory1, sub_directory2)
  ) %>% 
  arrange(desc(total_size)) %>% 
  # filter(n_files > 1) %>% 
  filter(total_size > fs_bytes("1G")) %>% 
  gt::gt() %>% 
  # gt::cols_width(
  #   starts_with("sub") ~ px(230),
  #   total_size ~ px(120)
  # ) %>% 
  gt::cols_align(align = "right", columns = total_size)

```




```{r}
paths_wes_seq <- 
  coghill_research_recurse_subdir %>% 
  filter(sub_directory2 %in% c("WES", "RNAseq")) %>% 
  pull(path)
  
everything_else <- 
  coghill_research_recurse %>% 
  unnest(dir_info) %>% 
  filter(!path %in% paths_wes_seq) %>% 
  summarise(
    n_files = n(),
    total_size = sum(size, na.rm = T),
    # .by = c(sub_directory1, sub_directory2)
  )
```

<br>

Not including WES and RNAseq data, all other files in *Coghill_Research* occupy 
`r paste0(everything_else$total_size, "B")` of storage space.


***

<br>
<br>

